CKY Parsing With Independence Constraints

### 2015-02-28 paper.tex
Minor changes
Minor edit

\label{sec:poly-classifier} For comparison with the linear classifier,
we trained another classifier using a polynomial kernel (with
degree 3) with all the features. The results are shown in Table
\ref{tbl:classifier-results-poly}. The polynomial kernel improves over
the linear classifier in accuracy by 2\%, in precision by 3 points, and
in recall by just over 13 points. This suggests that there is a large
potential for improving the linear classifier by adding conjunctive
features. Alternatively, there are methods for effectively linearizing
a kernel-based classifier, e.g. \cite{Kudo2003,Isozaki2002}.
Currently, the polynomial classifier takes over 2 hours to run on
section 22 (training the model took almost 4 days).

@@

To compare with previous work on parsing using the Penn Treebank, we
show the time and accuracy for parsing section 23, using both linear
and kernel classifier output, along with the baseline parser, below.
The times reported are the average of three runs each. Because there
was significant variation in parse time when multiple processes were
run in parallel, for these results only one process was run at a time.
 The results parallel those shown on the development data.

\begin{center}
\begin{tabular}{lrlrr}
parser & time (s) &  & F$_{\text{1}}$ & \\
\hline
baseline & 1538 &  & 85.54 & 0.00\\
linear & 1106 & \texttimes{}1.39 & 83.55 & -1.99\\
poly & 1040 & \texttimes{}1.48 & 84.57 & -0.97\\
\end{tabular}
\end{center}

>>>>

\label{sec:poly-classifier} For comparison with the linear classifier,
we trained another classifier using a polynomial kernel (with
degree 3) with all the features. The results are shown in Table
\ref{tbl:classifier-results-poly}. The polynomial kernel improves over
the linear classifier in accuracy by 2\%, in precision by 3 points, and
in recall by just over 13 points. This suggests that there is a large
potential for improving the linear classifier by adding conjunctive
features. Alternatively, there are methods for effectively linearizing
a kernel-based classifier \cite{Kudo2003,Isozaki2002}.
Currently, the polynomial classifier takes over 2 hours to run on
section 22 (training the model took almost 4 days).

@@

To compare with previous work on parsing using the Penn Treebank, we
show the time and accuracy for parsing section 23, using both linear
and kernel classifier output, along with the baseline parser, below.
The times reported are the average of three runs each. Because there
was significant variation in parse time when multiple processes were
run in parallel, for these results only one process was run at a time.
The results parallel those shown on section 22.

\begin{center}
\begin{tabular}{rc@{}lrr}
Parser & Time (s) &  & F$_{\text{1}}$ & \\
\hline
baseline & 1538 &  & 85.54 & 0.00\\
linear & 1106 & \texttimes{}1.39 & 83.55 & -1.99\\
poly & 1040 & \texttimes{}1.48 & 84.57 & -0.97\\
\end{tabular}
\end{center}
